---
title: "Introduction to ballr"
author: "Ryan Elmore"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ballr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Introduction 

Welcome to the ballr [**baw**-ler], as in baller^[https://www.urbandictionary.com/define.php?term=baller]. This is *the*
R resource for your basketball-reference.com needs. 

### Install the package
```{r, message = F, warning = F}
library(devtools)
devtools::install_github("rtelmore/ballr")
library(ballr)
```

<!-- ### Load some helpers -->

```{r, message = F, warning = F}
library(magrittr)
library(ggplot2)
library(janitor)
library(scales)
```

### Example 1
Current standings
```{r, message = F, warning = F}
standings <- NBAStandingsByDate() # "YEAR-MO-DY"
standings
```

Standings on an arbitrary date
```{r}
standings <- NBAStandingsByDate("2015-12-31")
standings
```

### Example 2
```{r}
players <- NBAPerGameStatistics()
players
```

### Example 3
```{r}
players <- NBAPerGameStatistics(season = 2017)
```
```{r}
players %>%
  dplyr::filter(mp > 20, pos %in% c("SF")) %>%
  dplyr::select(player, link) %>%
  dplyr::distinct()
```

### Example 4
```{r}
players <- NBAPerGameStatisticsPer36Min(season = 2017)
```
```{r}
players
```


### Example - Look at Centers and Power Forwards averaging more than 10 MPG
```{r}
players <- NBAPerGameStatisticsPer36Min(season = 2017) %>%
  dplyr::filter(pos %in% c("C", "PF")) %>%
  dplyr::top_n(n = 10, pts) %>% 
  dplyr::select(player, link) %>%
  dplyr::distinct()
```
```{r}
players
```

Query each player in the list
```{r}
player_stats <- NBAPlayerPerGameStats(players[1, 2]) %>%
  dplyr::filter(!is.na(age)) %>%
  dplyr::mutate(player = as.character(players[1, 1]))
```

Append the stats from each player into a df 
```{r}
for(i in 2:dim(players)[1]){
  tmp <- NBAPlayerPerGameStats(players[i, 2]) %>%
    dplyr::filter(!is.na(age)) %>%
    dplyr::mutate(player = as.character(players[i, 1]))
  player_stats <- dplyr::bind_rows(player_stats, tmp)
}
```

Plot everything
```{r}
#player_stats <- clean_names(player_stats)
p <- ggplot2::ggplot(data = player_stats,
            aes(x = age, y = efgpercent, group = player))
p + ggplot2::geom_line(alpha = .25) +
  ggplot2::geom_point(alpha = .25) +
  ggplot2::scale_y_continuous("effective field goal %age", limit = c(0, 1),
                     labels = percent) +
  ggplot2::geom_line(data = dplyr::filter(player_stats, player == "Anthony Davis"),
            aes(x = age, y = efgpercent), size = 1, col = "#1f78b4") +
  ggplot2::geom_point(data = dplyr::filter(player_stats, player == "Anthony Davis"),
            aes(x = age, y = efgpercent), size = 1, col = "#1f78b4") +
  ggplot2::geom_line(data = dplyr::filter(player_stats, player == "DeMarcus Cousins"),
            aes(x = age, y = efgpercent), size = 1, col = "#33a02c") +
  ggplot2::geom_point(data = dplyr::filter(player_stats, player == "DeMarcus Cousins"),
             aes(x = age, y = efgpercent), size = 1, col = "#33a02c") +
  ggplot2::theme_bw()

```

### Advanced Statistics
```{r}
per_100 <- NBAPerGameStatisticsPer100Poss(season = 2018)
utils::head(per_100)
```

### Advanced Statistics
```{r}
adv_stats <- NBAPerGameAdvStatistics(season = 2018)
utils::head(adv_stats)
```

### Example 
Look at selector gadget for a team's website, e.g. [Denver Nuggets](http://www.basketball-reference.com/teams/DEN/2017.html). Suppose you want to find everybody who played for the Nuggets last year, and then their stats. Remember to use Chrome (ugh). 
```{r}
library(rvest)

url <- "http://www.basketball-reference.com/teams/DEN/2017.html"
links <- xml2::read_html(url) %>%
    rvest::html_nodes(".center+ .left a") %>%
    rvest::html_attr('href')
```

```{r}
links 
```


